Number of COVID-19 Cases in Canada in 2022 By Region, Age, and Sex

### 2024-12-03 paper/paper.qmd
Updated prose

Another key advantage of the logistic regression model in this context is that it provides interpretable coefficients, which allow for an understanding of how specific predictors influence the odds of being high risk. This interpretability is crucial for public health applications. Furthermore, logistic regression is computationally efficient, making it ideal for datasets with relatively straightforward structures like this one. Thus, the logistic regression model strikes an appropriate balance between accuracy, interpretability, and simplicity, making it the most suitable choice for this analysis.

@@

Based on @fig-model_region, there is a higher density of individuals predicted to have high risk in the urban regions than in the rural regions. This disparity underscores the potential challenges faced by urban regions, such as overcrowding and not enough healthcare, which may contribute to higher case fatality rates (CFR). Since patients of COVID-19 were encouraged to stay at home even after testing positive at a hospital, patients who lived in urban regions may not have been able to access quick enough healthcare if their symptoms were to worsen rapidly. This could be reflected in the higher predicted risks for these communities. Overall, the predicted probability of high risk between the two regions were not much different, potentially reflecting that both regions experience certain challenges in healthcare and are similar in the amount and timeliness of healthcare received.

@@

The analysis revealed that there are no significant differences in predicted probability of high risk in males and females. The size of the difference is extremely small, especially compared to the IQR highlighted in @fig-model_sex. The potential differences can be attributed to biological differences, comorbidities, and health-seeking behaviors. There may be a slight difference between sexes in the sensitivity to one's own health conditions, willingness to seek healthcare, and other aspects. However, the analysis shows that the high risk is essentially equal for the two sexes. There is also an extremely large distribution of predicted probabilities within sexes as shown by the IQR. Therefore, more research and analysis will be needed to conclude that there are or are no sexual differences in the predicted probability of high risk.

@@

Another limitation is the reliance on aggregate data, which may obscure individual-level variability and interactions. For example, the interplay between age, sex, and comorbidities at the individual level could yield more nuanced insights. Additionally, the classification of rural and urban regions may oversimplify the diversity within these categories, such as the distinction between suburban and remote rural areas.

The patterns identified do not show strong correlations. The relationships between the key predictors (age, sex, and region) may not fully capture the complexity of the underlying risk factors. There could be additional variables that influence risk but were not included in this analysis. Furthermore, the correlations between these predictors and the high-risk classification may be influenced by other unmeasured or unobserved factors. These aspects of the dataset require further exploration in future research to better understand the full range of factors that contribute to COVID-19 risk and to refine the models used for risk classification.

@@

The database also ensures quality Control through running automated checks and manual reviews to detect inconsistencies, missing values, and potential errors in data entry. Such measures are crucial given the heterogeneity in reporting standards across countries and regions.

@@

"Thank you for participating in this study. The information you provided on demographic factors and the test done for COVID-19 positivity will help us better understand the impact of the pandemic across different demographic groups. Your responses will contribute to valuable research aimed at improving public health strategies. If you have any questions or would like further information about the study, please feel free to contact us at "brucejc.zhang\@mail.utoronto.ca"

>>>>

Another key advantage of the logistic regression model in this context is that it provides interpretable coefficients, which allow for an understanding of how specific predictors influence the odds of being high risk. This interpretability is very important for public health applications. Furthermore, logistic regression is computationally efficient, making it ideal for datasets with relatively straightforward structures like this one. Thus, the logistic regression model strikes an appropriate balance between accuracy, interpretability, and simplicity, making it the most suitable choice for this analysis.

@@

Based on @fig-model_region, there is a higher density of individuals predicted to have high risk in the urban regions than in the rural regions. This disparity underscores the potential challenges faced by urban regions, such as overcrowding and not enough healthcare, which may contribute to higher case fatality rates (CFR). Since patients of COVID-19 were encouraged to stay at home even after testing positive at a hospital, patients who lived in urban regions may not have been able to access quick enough healthcare if their symptoms were to worsen quickly. This could be reflected in the higher predicted risks for these communities. Overall, the predicted probability of high risk between the two regions were not much different, potentially reflecting that both regions experience certain challenges in healthcare and are similar in the amount and timeliness of healthcare received.

@@

The analysis showed no significant differences in predicted probability of high risk in males and females. The size of the difference is extremely small, especially compared to the IQR highlighted in @fig-model_sex. The potential differences can be attributed to biological differences, comorbidities, and health-seeking behaviors. There may be a slight difference between sexes in the sensitivity to one's own health conditions, willingness to seek healthcare, and other aspects. However, the analysis shows that the high risk is essentially equal for the two sexes. There is also an extremely large distribution of predicted probabilities within sexes as shown by the IQR. Therefore, more research and analysis will be needed to conclude that there are or are no sexual differences in the predicted probability of high risk.

@@

Another limitation is the reliance on aggregate data, which may obscure individual-level variability and interactions. For example, the interplay between age, sex, and comorbidities at the individual level could yield more relevant information. Additionally, the classification of rural and urban regions may oversimplify the diversity within these categories, such as the distinction between suburban and remote rural areas.

The patterns identified do not show strong correlations. The relationships between the key predictors (age, sex, and region) may not fully capture the complexity of the underlying risk factors. There could be additional variables that influence risk but were not included in this analysis. Furthermore, the correlations between these predictors and the high-risk classification may be influenced by other unmeasured or unobserved factors. These aspects of the dataset require further research to better understand the full range of factors that contribute to COVID-19 risk and to refine the models used for risk classification.

@@

The database also ensures quality Control through running automated checks and manual reviews to detect inconsistencies, missing values, and potential errors in data entry. Such measures are key given the heterogeneity in reporting standards across countries and regions.

@@

"Thank you for participating in this study. The information you provided on demographic factors and the test done for COVID-19 positivity will help us better understand the impact of the pandemic across different demographic groups. Your responses will contribute to research aimed at improving public health strategies. If you have any questions or would like further information about the study, please feel free to contact us at "brucejc.zhang\@mail.utoronto.ca"
